### 2020-08-27 neutronics.tex

Moltres solves the six-group neutron diffusion equations (Equation
\ref{eq:neut}) as a
steady-state eigenvalue problem to find the $k_{\text{eff}}$ for the static
\gls{MSFR} model. Table
\ref{table:keff} shows the $k_{\text{eff}}$ values from Serpent 2 and Moltres
at 973 K and the corresponding salt density, and Table \ref{table:ktemp} shows
the $k_{\text{eff}}$ values for other temperatures at 100 K intervals. Two
main factors contribute to the small discrepancies on the order of 100 pcm
between the two applications: the accuracy of the neutron diffusion
model, and the omission of the blanket tank structural material in Moltres.
The neutron diffusion model is not as accurate as the other S$_{\text{N}}$ or
SP$_{\text{N}}$ deterministic methods nor the Monte Carlo approach in Serpent.
Regarding the omission of the blanket tank material, I
replaced the 2 cm-thick structural material with blanket salt. This
replacement is partly responsible for the higher $k_{\text{eff}}$ value
calculated by Moltres as fissions occur in the blanket salt. Nevertheless, the
discrepancy is smaller
than the 228.5 pcm and 256.7 pcm discrepancies reported by Cervi et al.
\cite{cervi_development_2019} for their six-group $SP_3$ and neutron
diffusion methods, respectively.

@@

This work compares the $\beta$ value from Moltres to the
$\beta_{\text{eff}}$ value from Serpent because Moltres currently lacks an
adjoint calculation capability.
The difference between $\beta$ and $\beta_{\text{eff}}$ is
that $\beta$ is the unweighted delayed neutron fraction
while $\beta_{\text{eff}}$ is the delayed neutron fraction weighted by the
adjoint neutron flux. I calculated $\beta$ by
taking the relative difference between the $k_{\text{eff}}$ values with and
without \glspl{DNP} in Table \ref{table:keff}. The $\beta$ and
$\beta_{\text{eff}}$ values at 973 K, shown in Table \ref{table:betaeff}, are
in good agreement with a 4.43 pcm discrepancy.

@@

Temperature reactivity feedback arises mainly from Doppler broadening of
resonance absorption peaks and thermal expansion. The current work reports
the reactivity, $\rho$, values for temperatures from 800 K to 1400 K at 100 K
intervals (Figure \ref{fig:reactivity}). The slopes represent the total,
Doppler, density $\alpha$ values. The temperature range
extends below the melting point of the fuel salt (841 K) to ensure that
the data covers the relevant range between 841 K and 900 K. Table
\ref{table:alpha} shows the various $\alpha$ values calculated using the
linear least squares approach. The total temperature
coefficients from Serpent and Moltres show excellent agreement with a
discrepancy of 0.019 pcm K$^{-1}$.

@@

Moltres also closely replicated the six-group neutron spectrum from the
Serpent group constants. Figure \ref{fig:ntspec} compares the neutron energy
spectra from Serpent and Moltres in the central fuel salt region. More
generally, the
plot shows the distinctive fast spectrum observed in the \gls{MSFR} with dips
in the spectrum corresponding to elastic scattering resonances from lithium
and fluorine. From this plot, we observe that the discrepancies in
$k_{\text{eff}}$ arise mainly from discretizing neutron energy into groups
rather than the neutron diffusion model itself. We could obtain a more
accurate representation of the neutronics in the \gls{MSFR} by using more
neutron energy groups but this would adversely impact simulation times in the
subsequent multiphysics finite element analyses.

>>>>

Moltres solves the six-group neutron diffusion equations (Equation
\ref{eq:neut}) as a
steady-state eigenvalue problem to find the $k_{\text{eff}}$ for the static
\gls{MSFR} model. Table
\ref{table:keff} shows the $k_{\text{eff}}$ values from Serpent 2 and Moltres
at 973 K and the corresponding salt density, and Table \ref{table:ktemp} shows
the $k_{\text{eff}}$ values for other temperatures at 100 K intervals. Two
main factors contribute to the small discrepancies on the order of 100 pcm
between the two applications: the accuracy of the neutron diffusion
model, and the omission of the blanket tank structural material in Moltres.
The neutron diffusion model is not as accurate as the other S$_{\text{N}}$ or
SP$_{\text{N}}$ deterministic methods nor the Monte Carlo approach in Serpent.
Regarding the omission of the blanket tank material, this model
replaces the 2 cm-thick structural material with blanket salt. This
replacement is partly responsible for the higher $k_{\text{eff}}$ value
calculated by Moltres as fissions occur in the blanket salt. Nevertheless, the
discrepancy is smaller
than the 228.5 pcm and 256.7 pcm discrepancies reported by Cervi et al.
\cite{cervi_development_2019} for their six-group $SP_3$ and neutron
diffusion methods, respectively.

@@

This work compares the $\beta$ value from Moltres to the
$\beta_{\text{eff}}$ value from Serpent because Moltres currently lacks an
adjoint calculation capability.
The difference between $\beta$ and $\beta_{\text{eff}}$ is
that $\beta$ is the unweighted delayed neutron fraction
while $\beta_{\text{eff}}$ is the delayed neutron fraction weighted by the
adjoint neutron flux. This work calculates $\beta$ by
taking the relative difference between the $k_{\text{eff}}$ values with and
without \glspl{DNP} in Table \ref{table:keff}. The $\beta$ and
$\beta_{\text{eff}}$ values at 973 K, shown in Table \ref{table:betaeff}, are
in good agreement with a 4.43 pcm discrepancy.

@@

Temperature reactivity feedback arises mainly from Doppler broadening of
resonance absorption peaks and thermal expansion. The current work reports
the reactivity, $\rho$, values for temperatures from 800 K to 1400 K at 100 K
intervals (Figure \ref{fig:reactivity}). The slopes represent the total,
Doppler, density $\alpha$ values. The temperature range
extends below the melting point of the fuel salt (841 K) to ensure that
the data cover the relevant range between 841 K and 900 K. Table
\ref{table:alpha} shows the various $\alpha$ values calculated using the
linear least squares approach. The total temperature
coefficients from Serpent and Moltres show excellent agreement with a
discrepancy of 0.019 pcm K$^{-1}$.

@@

Moltres also closely replicated the six-group neutron spectrum from the
Serpent group constants. Figure \ref{fig:ntspec} compares the neutron energy
spectra from Serpent and Moltres in the central fuel salt region. More
generally, the
plot shows the distinctive fast spectrum observed in the \gls{MSFR} with dips
in the spectrum corresponding to elastic scattering resonances from lithium
and fluorine. We could obtain a more accurate representation of the neutronics
in the \gls{MSFR} by using more neutron energy groups with appropriate energy
boundaries but this would adversely impact simulation times in the
subsequent multiphysics finite element analyses.

### 2020-08-27 steadystate.tex

The procedure for obtaining the results for the steady-state operating
conditions involved several steps
due to the tightly coupled \glspl{PDE}. First, a preliminary transient
simulation of fluid flow in the \gls{MSFR} core was run, starting from zero
inlet velocity and gradually ramping up to match the nominal flow rate (4.5
m$^3$ s$^{-1}$); otherwise Moltres had difficulty converging to the desired
fully developed flow profile.
Next, these fully developed flow values were imported as initial values for
velocity in the full time-dependent simulation modeling the full coupled
neutronics and thermal-hydraulics multiphysics model. The initial values for
the temperature and neutron group flux distributions are 953 K and
$1 \times 10^{14}$ cm$^{-2}$ s$^{-1}$ uniformly throughout the geometry.
Finally, this work assumes that steady state is reached when the volume
integral values of every variable remain constant (up to 6 significant
figures) for at least four seconds in the simulation; this
time period corresponds to the nominal circulation time of the \gls{MSFR}.

@@

Figure \ref{fig:flow-temp} shows the temperature and velocity fields of the
fuel salt in the core at steady state from Moltres and the Polimi and TUDelft
models. Figure \ref{fig:flow} provides an alternate view of the flow profile
through flow streamlines superimposed on the velocity magnitude distribution.
The results from Moltres show good qualitative agreement with the Polimi and
TUDelft models \cite{fiorina_modelling_2014}; the plots show similar
flow and hotspot features in all three models. Furthermore, the highest salt
velocities in all three models occur at the inlet, outlet, and at core
half-height approximately 0.40 m away from the central axis. A large
recirculation region forms near the blanket tank walls from turbulent flow.
Inertial forces dominate over viscous forces to form this large eddy. The main
difference between Moltres, and the Polimi and TUDelft models is the flow
profile near the central axis at the top and bottom of the core.
The Polimi and TUDelft models predict relatively stagnant flow in these
regions without recirculation. Moltres, on the other hand, predicts explicit
recirculating flow in these regions. This is due to our constant turbulent
viscosity approximation in Moltres. The k-$\epsilon$ turbulence models in the
Polimi and TUDelft models predict that the turbulent viscosity in these
regions is as high as 100 Pa$\cdot$s, much higher than our 40 Pa$\cdot$s
approximation.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.58\textwidth]{flow-plasma}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core.
    The colors represent velocity magnitude according to the color bar on the
    right.}
    \label{fig:flow}
\end{figure}

@@

Although the temperatures at the hotspots are well below the melting point of the Ni-alloy structure (1500 K), they may cause undue thermal stress on the
blanket tank structure and accelerate salt corrosion rates. A
sudden, large reactivity insertion could push fuel salt temperatures above the
melting point of the Ni-alloy and cause irreversible damage. Furthermore,
the reservoir of hot fuel salt may cause unpredictable behavior during
transient scenarios when the flow profile fluctuates.
Thus, Rouch et al. \cite{rouch_preliminary_2014} developed an improved
hourglass-shaped design for the central core region to optimize flow
distribution and prevent these
recirculation zones and hotspots from forming. A study of this new design
using Moltres is a potential subject for future work when a proper turbulence
model is in place.

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g3}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g4}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g5}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g6}
    \end{subfigure}
    \caption{Neutron flux distributions in the core for neutron energy groups
    1 to 6. The y and x axes represent height and radius (in cm) of the core
    relative to the entire reactor geometry.}
    \label{fig:neutronflux}
\end{figure}

@@

\begin{table}[b!]
	\centering
	\caption{Peak neutron flux values from Moltres (this paper), COMSOL
	\cite{fiorina_molten_2013}, and OpenFOAM \cite{aufiero_development_2014}
	models along with the temperature distribution with which the values were
	obtained.}
	\begin{tabular}{l l S}
		\toprule
		{Model} & {Temperature distribution} & {Peak Neutron Flux [$\times 10^{15}$ cm$^{-2}$ s$^{-1}$]}
		\\
		\midrule
		{Moltres (This paper)} & {Steady state} & 9.80\\
		{COMSOL} & {Uniform, 973 K} & 8.6 \\
		{OpenFOAM} & {Uniform, 973 K} & 9.0 \\
		\bottomrule
	\end{tabular}
	\label{table:peak-flux}
\end{table}

@@

As mentioned earlier, the delayed neutron precursors (DNPs) are mobile in
\glspl{MSR} and their distributions do not directly correspond to the neutron
flux distributions. The location where the \glspl{DNP} decay and emit neutrons
impacts their neutron
importance depending on their proximity to fissile and parasitic isotopes.
Figure \ref{fig:dnp} shows the \gls{DNP} distributions for all eight \gls{DNP}
groups. In general, the figures show less \glspl{DNP} in the regions with fast
salt flow. The
precursors from the shortest-lived group (Group 8) predominantly decay within
the core as their half-lives are shorter than the time it takes to reach the
outlet while the precursors from the longest-lived group (Group 1) are
relatively evenly distributed due to their long half-lives. For the
longer-lived groups, the \gls{DNP} concentrations are ill-resolved on the
mesh elements adjacent to the outlet and the inlet boundaries, respectively.
Thus, the present author recommends careful mesh refinement for future work
involving similar geometries.

@@

The in-core delayed neutron fraction, which we denote as $\beta_c$, is an
important safety parameter for \glspl{MSR}. This value represents the actual
delayed neutron fraction in \glspl{MSR} after accounting for the loss of
delayed neutrons from \glspl{DNP} decaying outside the active core region.
Reactors with smaller $\beta$ values exhibit greater prompt jumps in the
neutron flux in response to reactivity insertions because they have a greater
proportion of prompt neutrons under normal operating conditions. This is
undesirable from a reactor safety perspective because it reduces the time
available for active safety mechanisms to
activate and scram the reactor. In \glspl{MSR}, this danger is partly
mitigated by the strong, negative fuel temperature reactivity coefficient. 
Chapter 6 contains more in-depth discussions for various transient scenarios.

@@

The fraction of out-of-core emissions from our Moltres model
differs significantly by approximately 10\%, and $\beta_c$ differs by
60-70 pcm. The former is attributed to the lesser \gls{DNP} retention in the
stagnant flow regions in the core; the \glspl{DNP} are more evenly distributed
along the entire primary loop and a greater fraction of delayed neutron
emissions occur in the outer loop region. The flow patterns are responsible
for the distribution of shorter-lived \gls{DNP} since convection is the
dominant mode of species transport in the \gls{MSFR}. The exact flow pattern
in the recirculation zones in the Polimi and TUDelft models differs from
that in Moltres (Figure \ref{fig:flow}). Figure \ref{fig:flow-temp} also shows
some minor differences in the magnitude of the flow in the recirculation zones
between Moltres, and the Polimi and TUDelft models. Although the sizes of the
arrows representing flow velocity are on different scales, a
quick comparison between the largest arrows and the arrows in the
recirculation zone indicates that the recirculation zone in Moltres is
more stagnant. This could explain the concentration of \glspl{DNP}
along an ``arc'' closer to the center of the core in Moltres as opposed to the
more even distribution of \glspl{DNP} throughout the whole recirculation zones
in the Polimi and TUDelft models. The higher peak \gls{DNP} distribution in
Moltres also supports this assertion.

In spite of the greater delayed neutron losses, the $\beta_c$ value is higher
in Moltres than the Polimi and TUDelft models. Fiorina et al.
\cite{fiorina_modelling_2014} applied adjoint flux
weighting for their $\beta_c$ calculation whereas this work
reports the value as the physical fraction without adjoint weighting. The
weighting results in a significant difference in $\beta_c$ because a greater
fraction of the \glspl{DNP} decay in the recirculation zones, where the
neutron importance is noticeably diminished.

@@

Figure \ref{fig:decayheattemp} shows the
difference in core temperatures at steady state with decay heat modeling
relative to the core temperatures without decay heat in Figure
\ref{fig:flow-temp}. This figure uses a different color map to clearly
distinguish between positive and negative temperature differences in the core.
The hotspots in the recirculation zones are approximately
2 to 4 K cooler, while the cooled salt flowing in from the inlet is
approximately 2 K hotter. These regions correspond to the hottest and coldest
areas in the core and the results agree with the expectation that the extreme
temperatures would be affected the most by the introduction of decay heat
precursors. The difference between the outlet and inlet temperatures falls
from 101.1 K to 98.9 K as some of the decay heat precursors deposit heat in
the outer loop region. The figure also shows some nonphysical oscillations in
the temperature near the outlet because the mesh near the boundary is too
coarse for the given outlet velocities. Users can avoid these oscillations
near the outlet by using a mesh
that is progressively finer towards the boundary. The
present author could not resolve this issue due to time constraints.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.55\textwidth]{decay-heat-temp}
    \caption{Difference in core temperatures at steady state with decay heat
    relative to the result without decay heat (Figure \ref{fig:flow-temp}).}
    \label{fig:decayheattemp}
\end{figure}

>>>>

The procedure for obtaining the results for the steady-state operating
conditions involved several steps
due to the tightly coupled \glspl{PDE}. First, a preliminary transient
simulation of fluid flow in the \gls{MSFR} core was run, starting from zero
inlet velocity and gradually ramping up to match the nominal flow rate (4.5
m$^3$ s$^{-1}$); otherwise Moltres had difficulty converging to the desired
fully developed flow profile.
Next, these fully developed flow values were imported as initial values for
velocity in the full time-dependent simulation modeling the full coupled
neutronics and thermal-hydraulics multiphysics model. The initial values for
the temperature and neutron group flux distributions are 953 K and
$1 \times 10^{14}$ cm$^{-2}$ s$^{-1}$ uniformly throughout the geometry.
Finally, this work assumes that model has reached steady-state when the volume
integral values of every variable remain constant (up to 6 significant
figures) for at least four seconds in the simulation; this
period of time corresponds to the nominal circulation time of the \gls{MSFR}.

@@

Figure \ref{fig:flow-temp} shows the temperature and velocity fields of the
fuel salt in the core at steady-state from Moltres and the Polimi and TUDelft
models. Figure \ref{fig:flow} provides an alternate view of the flow profile
with flow streamlines superimposed on the velocity magnitude distribution.
The results from Moltres show good qualitative agreement with the Polimi and
TUDelft models \cite{fiorina_modelling_2014}; the plots show similar
flow and hotspot features in all three models. Furthermore, the highest salt
velocities in all three models occur at the inlet, outlet, and at core
half-height approximately 0.40 m away from the central axis. A large
recirculation region forms near the blanket tank walls. The main
difference between Moltres, and the Polimi and TUDelft models is the flow
profile near the central axis at the top and bottom of the core.
The Polimi and TUDelft models predict relatively stagnant flow in these
regions without recirculation. Moltres, on the other hand, predicts explicit
recirculating flow in these regions. This is due to our constant turbulent
viscosity approximation in Moltres. The k-$\epsilon$ turbulence models in the
Polimi and TUDelft models predict that the turbulent viscosity in these
regions is as high as 100 Pa$\cdot$s, much higher than our 40 Pa$\cdot$s
approximation.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.58\textwidth]{flow-plasma}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core
    from Moltres.
    The colors represent velocity magnitude according to the color bar on the
    right.}
    \label{fig:flow}
\end{figure}

@@

Although the temperatures at the hotspots are well below the melting point of
the Ni-alloy structure (1500 K), they may cause undue thermal stress on the
blanket tank structure and accelerate salt corrosion rates. A
sudden, large reactivity insertion could push fuel salt temperatures above the
melting point of the Ni-alloy and cause irreversible damage. Furthermore,
the reservoir of hot fuel salt may cause unpredictable behavior during
transient scenarios when the flow profile fluctuates.

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g3}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g4}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g5}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g6}
    \end{subfigure}
    \caption{Neutron flux distributions in the core for neutron energy groups
    1 to 6. The y and x axes represent height and radius (in cm) of the core
    relative to the entire reactor geometry. Note the different scales for
    each flux distribution.}
    \label{fig:neutronflux}
\end{figure}

@@

\begin{table}[b!]
	\centering
	\caption{Peak neutron flux values from Moltres (this paper), COMSOL
	\cite{fiorina_molten_2013}, and OpenFOAM \cite{aufiero_development_2014}
	models along with the temperature distribution with which the values were
	obtained.}
	\begin{tabular}{l l S}
		\toprule
		{Model} & {Temperature distribution} & {Peak Neutron Flux [$\times 10^{15}$ cm$^{-2}$ s$^{-1}$]}
		\\
		\midrule
		{Moltres (This paper)} & {Steady-state} & 9.80\\
		{COMSOL} & {Uniform, 973 K} & 8.6 \\
		{OpenFOAM} & {Uniform, 973 K} & 9.0 \\
		\bottomrule
	\end{tabular}
	\label{table:peak-flux}
\end{table}

@@

As mentioned earlier, the delayed neutron precursors (DNPs) are mobile in
\glspl{MSR} and their distributions do not directly correspond to the neutron
flux distributions. The location where the \glspl{DNP} decay and emit neutrons
impacts their neutron
importance depending on their proximity to fissile and parasitic isotopes.
Figure \ref{fig:dnp} shows the \gls{DNP} distributions for all eight \gls{DNP}
groups. In general, the figures show less \glspl{DNP} in the regions with fast
salt flow. The
precursors from the shortest-lived group (Group 8) predominantly decay within
the core as their half-lives are shorter than the time it takes to reach the
outlet while the precursors from the longest-lived group (Group 1) are
relatively evenly distributed due to their long half-lives. For the
longer-lived groups, the \gls{DNP} concentrations are ill-resolved on the
mesh elements adjacent to the outlet and the inlet boundaries.
Thus, the present author recommends careful mesh refinement for future work
involving similar geometries.

@@

The in-core delayed neutron fraction, which we denote as $\beta_c$, is an
important safety parameter for \glspl{MSR}. This value represents the actual
delayed neutron fraction in \glspl{MSR} after accounting for the loss of
delayed neutrons from \glspl{DNP} decaying outside the active core region.
Reactors with smaller $\beta$ values exhibit greater prompt jumps in the
neutron flux in response to reactivity insertions because they have a greater
proportion of prompt neutrons under normal operating conditions. This effect
is undesirable from a reactor safety perspective because it reduces the time
available for active safety mechanisms to
activate and scram the reactor. In \glspl{MSR}, the strong, negative fuel
temperature reactivity coefficient partly mitigates the sharp increase in
neutron flux. 
Chapter 6 contains more in-depth discussions for various transient scenarios.

@@

The fraction of out-of-core emissions from the Moltres model
differs significantly by approximately 10\%, and $\beta_c$ differs by
60-70 pcm. The former is attributed to the lesser \gls{DNP} retention in the
stagnant flow regions in the core; the \glspl{DNP} are more evenly distributed
along the entire primary loop and a greater fraction of delayed neutron
emissions occur in the outer loop region. The flow patterns are responsible
for the distribution of shorter-lived \gls{DNP} since convection is the
dominant mode of species transport in the \gls{MSFR}. The exact flow pattern
in the recirculation zones in the Polimi and TUDelft models differs from
that in Moltres (Figure \ref{fig:flow}). Figure \ref{fig:flow-temp} also shows
some minor differences in the magnitude of the flow in the recirculation zones
between Moltres, and the Polimi and TUDelft models. Although the sizes of the
arrows representing flow velocity are on different scales, a
quick comparison between the largest arrows and the arrows in the
recirculation zone indicates that the recirculation zone in Moltres is
more stagnant. This could explain the concentration of \glspl{DNP}
along an ``arc'' closer to the center of the core in Moltres as opposed to the
more even distribution of \glspl{DNP} throughout the whole recirculation zones
in the Polimi and TUDelft models. The higher peak \gls{DNP} distribution in
Moltres also supports this assertion.

In spite of the greater delayed neutron losses, the $\beta_c$ value is higher
in Moltres than the Polimi and TUDelft models. Fiorina et al.
\cite{fiorina_modelling_2014} applied adjoint flux
weighting for their $\beta_c$ calculation whereas this work
reports the value as the physical fraction without adjoint weighting. The
adjoint weighting results in a smaller $\beta_c$ because a greater
fraction of the \glspl{DNP} decay in the recirculation zones, where the
neutron importance is noticeably diminished. Fast reactors also typically have
smaller $\beta_{\text{eff}}$ because the fission cross sections of fertile
isotopes (e.g. $^{238}$U and $^{232}Th$) monotonically decrease with
decreasing neutron energy \cite{ott_introductory_1985}. On average, delayed
neutrons are less energetic than prompt neutrons.

@@

Figure \ref{fig:decayheattemp} shows the
difference in core temperatures at steady-state with decay heat modeling
relative to the core temperatures without decay heat in Figure
\ref{fig:flow-temp}. This figure uses a different color map to clearly
distinguish between positive and negative temperature differences in the core.
The hotspots in the recirculation zones are approximately
2 to 4 K cooler, while the cooled salt flowing in from the inlet is
approximately 2 K hotter. These regions correspond to the hottest and coldest
areas in the core and the results agree with the expectation that the extreme
temperatures would be affected the most by the introduction of decay heat
precursors. The difference between the outlet and inlet temperatures falls
from 101.1 K to 98.9 K as some of the decay heat precursors deposit heat in
the outer loop region. The figure also shows some nonphysical oscillations in
the temperature near the outlet because the mesh near the boundary is too
coarse for the given outlet velocities. Users can avoid these oscillations
near the outlet by using a mesh that is progressively finer towards the
boundary. This exercise is left as an objective for future work.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.55\textwidth]{decay-heat-temp}
    \caption{Difference in core temperatures at steady-state with decay heat
    relative to the result without decay heat (Figure \ref{fig:flow-temp}).}
    \label{fig:decayheattemp}
\end{figure}
